Output Summary

### 2021-08-03 03-post-process/output-plots.Rmd
Update all fit diagnostic plots to show multiple populations

# Fit to Data {.tabset .tabset-pills}

In the figures below, the thick red line is the posterior median value each year, the red region is the equal-tailed 95% credible interval, and blue points are "observed" data (estimated from raw data external to the model).

## Abundance Data

```{r abundance-data-fits, fig.width = 3, fig.height = 5}
par(mfcol = c(3,1), oma = c(1.5,1.5,0,0))
plot_tseries(post_summ(post, "^Pa[.+,1]$"), jags_data$Pa_obs[observable,1], main = TeX("$Fall\\,Parr\\,Abundance\\,(At\\,Trap)$"))
plot_tseries(post_summ(post, "^Mb[.+,2,1]$"), jags_data$Mb_obs[observable,2,1], main = TeX("$Spring\\,Smolt\\,Abundance\\,(At\\,Trap)$"))
plot_tseries(post_summ(post, "^Ra_tot["), jags_data$Ra_obs[observable], main = TeX("$Adult\\,Return\\,Abundance$"))

mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Abundance")
```

## Survival Data

```{r survival-data-fits, fig.width = 5, fig.height = 6}
par(mfcol = c(3,2), oma = c(1.5,1.5,0,0))
plot_tseries(post_summ(post, "^phi_Pb_Ma["), expit(jags_data$Lphi_obs_Pb_Ma[observable]), main = TeX("$Summer\\,Parr \\rightarrow LGR"))
plot_tseries(post_summ(post, "^phi_Pa_Ma[.+,1]$"), expit(jags_data$Lphi_obs_Pa_Ma[observable,1]), main = TeX("$Fall\\,Parr \\rightarrow LGR"))
plot_tseries(post_summ(post, "^phi_Mb_Ma[.+,2,1]$"), expit(jags_data$Lphi_obs_Mb_Ma[observable,2,1]), main = TeX("$Spring\\,Smolt \\rightarrow LGR\\,(NOR)"))
plot_tseries(post_summ(post, "^phi_Mb_Ma[.+,2,2]$"), expit(jags_data$Lphi_obs_Mb_Ma[observable,2,2]), main = TeX("$Spring\\,Smolt \\rightarrow LGR\\,(HOR)"))
plot_tseries(post_summ(post, "^phi_Ma_O0[.+,1]$"), expit(jags_data$Lphi_obs_Ma_O0[observable,1]), main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,(NOR)"))
plot_tseries(post_summ(post, "^phi_Ma_O0[.+,2]$"), expit(jags_data$Lphi_obs_Ma_O0[observable,2]), main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,(HOR)"))
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

## Composition Data {.tabset .tabset-pills .tabset-fade}

Within a single year, the values across all panels sum to one.

### Weir Sampling

```{r weir-comp-data-fits, fig.width = 8, fig.height = 5}
# calculate observed q
q_obs = t(apply(jags_data$weir_x_obs, 1, function(y) y/sum(y)))

par(mfcol = c(3,4), oma = c(1.5,1.5,0,0))#, mar = c(1.5,1.5,1.5,0.5))
plot_tseries(post_summ(post, "^q_Ra[.+,1]$"), q_obs[observable,1], main = TeX("$Female\\,Age\\,3\\,(NOR)$"))
plot_tseries(post_summ(post, "^q_Ra[.+,2]$"), q_obs[observable,2], main = TeX("$Female\\,Age\\,4\\,(NOR)$"))
plot_tseries(post_summ(post, "^q_Ra[.+,3]$"), q_obs[observable,3], main = TeX("$Female\\,Age\\,5\\,(NOR)$"))
plot_tseries(post_summ(post, "^q_Ra[.+,4]$"), q_obs[observable,4], main = TeX("$Male\\,Age\\,3\\,(NOR)$"))
plot_tseries(post_summ(post, "^q_Ra[.+,5]$"), q_obs[observable,5], main = TeX("$Male\\,Age\\,4\\,(NOR)$"))
plot_tseries(post_summ(post, "^q_Ra[.+,6]$"), q_obs[observable,6], main = TeX("$Male\\,Age\\,5\\,(NOR)$"))
plot_tseries(post_summ(post, "^q_Ra[.+,7]$"), q_obs[observable,7], main = TeX("$Female\\,Age\\,3\\,(HOR)$"))
plot_tseries(post_summ(post, "^q_Ra[.+,8]$"), q_obs[observable,8], main = TeX("$Female\\,Age\\,4\\,(HOR)$"))
plot_tseries(post_summ(post, "^q_Ra[.+,9]$"), q_obs[observable,9], main = TeX("$Female\\,Age\\,5\\,(HOR)$"))
plot_tseries(post_summ(post, "^q_Ra[.+,10]$"), q_obs[observable,10], main = TeX("$Male\\,Age\\,3\\,(HOR)$"))
plot_tseries(post_summ(post, "^q_Ra[.+,11]$"), q_obs[observable,11], main = TeX("$Male\\,Age\\,4\\,(HOR)$"))
plot_tseries(post_summ(post, "^q_Ra[.+,12]$"), q_obs[observable,12], main = TeX("$Male\\,Age\\,5\\,(HOR)$"))
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
```

### Carcass Sampling

```{r carc-comp-data-fits, fig.width = 8, fig.height = 5}
# calculate observed q
q_obs = t(apply(jags_data$carc_x_obs, 1, function(y) y/sum(y)))

par(mfcol = c(3,4), oma = c(1.5,1.5,0,0))
plot_tseries(post_summ(post, "^q_Sa_adj[.+,1]$"), q_obs[observable,1], main = TeX("$Female\\,Age\\,3\\,(NOR)$"))
plot_tseries(post_summ(post, "^q_Sa_adj[.+,2]$"), q_obs[observable,2], main = TeX("$Female\\,Age\\,4\\,(NOR)$"))
plot_tseries(post_summ(post, "^q_Sa_adj[.+,3]$"), q_obs[observable,3], main = TeX("$Female\\,Age\\,5\\,(NOR)$"))
plot_tseries(post_summ(post, "^q_Sa_adj[.+,4]$"), q_obs[observable,4], main = TeX("$Male\\,Age\\,3\\,(NOR)$"))
plot_tseries(post_summ(post, "^q_Sa_adj[.+,5]$"), q_obs[observable,5], main = TeX("$Male\\,Age\\,4\\,(NOR)$"))
plot_tseries(post_summ(post, "^q_Sa_adj[.+,6]$"), q_obs[observable,6], main = TeX("$Male\\,Age\\,5\\,(NOR)$"))
plot_tseries(post_summ(post, "^q_Sa_adj[.+,7]$"), q_obs[observable,7], main = TeX("$Female\\,Age\\,3\\,(HOR)$"))
plot_tseries(post_summ(post, "^q_Sa_adj[.+,8]$"), q_obs[observable,8], main = TeX("$Female\\,Age\\,4\\,(HOR)$"))
plot_tseries(post_summ(post, "^q_Sa_adj[.+,9]$"), q_obs[observable,9], main = TeX("$Female\\,Age\\,5\\,(HOR)$"))
plot_tseries(post_summ(post, "^q_Sa_adj[.+,10]$"), q_obs[observable,10], main = TeX("$Male\\,Age\\,3\\,(HOR)$"))
plot_tseries(post_summ(post, "^q_Sa_adj[.+,11]$"), q_obs[observable,11], main = TeX("$Male\\,Age\\,4\\,(HOR)$"))
plot_tseries(post_summ(post, "^q_Sa_adj[.+,12]$"), q_obs[observable,12], main = TeX("$Male\\,Age\\,5\\,(HOR)$"))
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
```

## Spawn Status Data

```{r spawn-status-fits, fig.width = 3.5, fig.height = 5}
par(oma = c(1.5,1.5,0,0))
layout(matrix(c(1,2), 2, 1), heights = c(1, 0.65))
plot_tseries(post_summ(post, "^phi_Sb_Sa["), with(jags_data, carcs_spawned/carcs_sampled)[observable], main = "Successful Spawning")
mtext(side = 2, "Survival Probability", line = 1.5)

at_x = seq(1, length(observable), 4)
par(mar = c(2,2,0,1), yaxs = "i")
mp = barplot(jags_data$carcs_sampled[observable], xaxt = "n", ylim = c(0, max(jags_data$carcs_sampled, na.rm = T)) + c(0, 5))
axis(side = 1, at = mp[at_x], labels = substr( names(jags_data$carcs_sampled[observable]), 3, 4)[at_x])
box()
mtext(side = 2, "Carcasses Sampled", line = 1.5)
mtext(side = 1, "Brood Year", line = 1.5)
```

@@

```{r eggs-to-parr, fig.width = 6, fig.height = 4}
# extract posterior samples of the BH productivity and capacity parameters
bh_params = post_subset(post, c("alpha", "^beta$"), matrix = T)

# extract posterior summaries of total spawners by brood year
Sa_tot = post_summ(post, "^Sa_tot[")

# extract posterior summaries of total egg production by brood year
f_tot = post_summ(post, "^f_tot[")

# predict parr recruits along a sequence of spawner abundances
Sa_pred = seq(0, max(Sa_tot[5,]), length = 30)
f_pred = seq(0, max(f_tot[5,]), length = 30)

Pb_pred = t(sapply(1:post_dim(post, "saved"), function(i) BH(f_pred, bh_params[i,1], bh_params[i,2])))
colnames(Pb_pred) = paste0("Pb_pred[", 1:length(Sa_pred), "]")
Pb_pred = post_convert(cbind(postpack:::id_mat(post), Pb_pred))
Pb_pred = post_summ(Pb_pred, "Pb_pred")

# fit ordinary least squares version
ols_fit = fit_fecund_BH(jags_data)$BH_fit

# draw 1000 random parameters
ols_params = exp(rmvnorm(1000, coef(ols_fit), vcov(ols_fit)))

# calculate predicted curve at each pair/summarize
ols_R_pred = t(sapply(1:1000, function(i) BH(f_pred, ols_params[i,1], ols_params[i,2])))
ols_R_pred = apply(ols_R_pred, 2, function(x) quantile(x, c(0.5, 0.025, 0.975)))

# graphical parameters
par(mar = c(3,3,1,1), mgp = c(2,0.3,0), tcl = -0.2)

# empty plot
plot(1, 1, type = "n", xlim = range(0, f_tot[5,]), ylim = range(0, Pb[5,], Pb_pred[5,]),
     xlab = "Total Egg Production (millions)", ylab = "Parr Recruits", xaxt = "n")

x_ticks = axisTicks(par("usr")[1:2], log = F)
axis(side = 1, at = x_ticks, labels = x_ticks/1e6)

# draw fitted relationship: Bayesian
polygon(c(f_pred, rev(f_pred)), c(Pb_pred[4,], rev(Pb_pred[5,])), col = alpha("salmon", 0.5), border = NA)
lines(Pb_pred[4,] ~ f_pred, col = "red", lty = 2)
lines(Pb_pred[5,] ~ f_pred, col = "red", lty = 2)

# draw fitted relationship: OLS
polygon(c(f_pred, rev(f_pred)), c(ols_R_pred[2,], rev(ols_R_pred[3,])), col = alpha("grey", 0.5), border = NA)
lines(ols_R_pred[1,] ~ f_pred, lwd = 2)
lines(ols_R_pred[2,] ~ f_pred, lty = 2)
lines(ols_R_pred[3,] ~ f_pred, lty = 2)
lines(Pb_pred[3,] ~ f_pred, col = "red", lwd = 2)

# draw state pairs + uncertainty
segments(f_tot[4,], Pb[3,], f_tot[5,], Pb[3,], col = "red")
segments(f_tot[3,], Pb[4,], f_tot[3,], Pb[5,], col = "red")
points(Pb[3,] ~ f_tot[3,], pch = 21, col = "red", bg = alpha("salmon", 0.5))
```

## Total Eggs vs. Total Spawners

This figure illustrates that total spawners is a reasonable index of total egg production. The three lines illustrate the relationship if each spawner (regardless of age/sex) had a fixed number of eggs.

```{r, fig.width = 6, fig.height = 4}
# extract posterior summaries of total egg production by brood year
f_tot = post_summ(post, "^f_tot[")

# extract posterior summaries of total spawners by brood year
Sa_tot = post_summ(post, "^Sa_tot[")

par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(3,3,1,1))
plot(f_tot["mean",] ~ Sa_tot["mean",],
     ylim = c(0, max(f_tot["97.5%",])),
     xlim = c(0, max(Sa_tot["97.5%",])), type = "n",
     ylab = "Total Egg Production (Millions)", xlab = "Total Spawners", las = 1, yaxt = "n")
y_ticks = axisTicks(par("usr")[3:4], log = F)
axis(side = 2, at = y_ticks, labels = y_ticks/1e6, las = 2)

segments(Sa_tot["2.5%",], f_tot["mean",], Sa_tot["97.5%",], f_tot["mean",], col = alpha("red", 0.5))
segments(Sa_tot["mean",], f_tot["2.5%",], Sa_tot["mean",], f_tot["97.5%",], col = alpha("red", 0.5))
points(f_tot["mean",] ~ Sa_tot["mean",], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
abline(c(0, 1000), lty = 1)
abline(c(0, 1800), lty = 2)
abline(c(0, 3600), lty = 3)
legend("bottomright", title = "If Each Spawner Had:",
       legend = c("1000 Eggs", "1800 Eggs", "3600 Eggs"),
       lty = c(1,2,3), bty = "n")
```

@@

This figure shows the inherent density dependence built in to the Beverton-Holt recruitment function: with increasing egg density, survival per egg decreases. The horizontal line/region shows the theoretical maximum ($\alpha$) in the absence of density dependence.

```{r, fig.width = 6, fig.height = 4}
# extract posterior summaries of total egg production by brood year
f_tot = post_summ(post, "^f_tot[")

# conversion rates
Pb_per_f_tot = post_summ(post, "^Pb_per_f_tot[")

# max survival
alpha = post_summ(post, "^alpha")

par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(3,3,1,1))
plot(Pb_per_f_tot["mean",] ~ f_tot["mean",],
     ylim = c(0, max(Pb_per_f_tot["97.5%",], alpha["97.5%",])),
     xlim = c(0, max(f_tot["97.5%",])), type = "n",
     ylab = "Parr per Egg", xlab = "Total Egg Production (Millions)", las = 1, xaxt = "n")
x_ticks = axisTicks(par("usr")[1:2], log = F)
axis(side = 1, at = x_ticks, labels = x_ticks/1e6)

segments(f_tot["2.5%",], Pb_per_f_tot["mean",], f_tot["97.5%",], Pb_per_f_tot["mean",], col = alpha("red", 0.5))
segments(f_tot["mean",], Pb_per_f_tot["2.5%",], f_tot["mean",], Pb_per_f_tot["97.5%",], col = alpha("red", 0.5))
points(Pb_per_f_tot["mean",] ~ f_tot["mean",], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)

rect(par("usr")[1], alpha["2.5%",], par("usr")[2], alpha["97.5%",], border = alpha("red", 0.5), col = alpha("salmon", 0.5))
abline(h = alpha["mean",], lwd = 2, col = "red")
box()
```

>>>>

# Fit to Data

In all figures below, the thick red line is the posterior median value each year, the red region is the equal-tailed 95% credible interval, and blue points are "observed" data (estimated from raw data external to the model).

## Abundance Data {.tabset .tabset-pills}

### Fall Parr Abundance

```{r fall-trap-N-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^Pa[.+,LH_type,pop]$", LH_type = i_fall, pop = j)), jags_data$Pa_obs[observable,i_fall,j], main = pops[j])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Fall Parr Abundance")
```

### Spring Smolt Abundance

```{r spring-trap-N-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^Mb[.+,LH_type,origin,pop]$", origin = o_nor, LH_type = i_spring, pop = j)), jags_data$Mb_obs[observable,i_spring,o_nor,j], main = pops[j])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Spring Smolt Abundance")
```

### Adult Return Abundance

```{r adult-N-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^Ra_tot[.+,pop]$", pop = j)), jags_data$Ra_obs[observable,j], main = pops[j])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Return Year")
mtext(side = 2, outer = T, line = 0.25, "Adult Return Abundance")
```

## Survival Data {.tabset .tabset-pills}

### Summer Parr $\rightarrow$ LGR

```{r summer-surv-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_Pb_Ma[.+,pop]", pop = j)), expit(jags_data$Lphi_obs_Pb_Ma[observable,j]), main = pops[j])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, TeX("$Summer\\,Parr \\rightarrow LGR\\,Survival$"))
```

### Fall Parr $\rightarrow$ LGR

```{r fall-surv-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_Pa_Ma[.+,LH_type,pop]$", LH_type = i_fall, pop = j)), expit(jags_data$Lphi_obs_Pa_Ma[observable,i_fall,j]), main = pops[j])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, TeX("$Fall\\,Parr \\rightarrow LGR\\,Survival$"))
```

### Spring Smolt $\rightarrow$ LGR (NOR)

```{r spring-surv-fit-nor, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_Mb_Ma[.+,LH_type,origin,pop]$",LH_type = i_spring, origin = o_nor, pop = j)), expit(jags_data$Lphi_obs_Mb_Ma[observable,i_spring,o_nor,j]), main = pops[j])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, TeX("$Spring\\,Smolt \\rightarrow LGR\\,Survival\\,(NOR)$"))
```

### Spring Smolt $\rightarrow$ LGR (HOR)

```{r spring-surv-fit-hor, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_Mb_Ma[.+,LH_type,origin,pop]$", LH_type = i_spring, origin = o_hor, pop = j)), expit(jags_data$Lphi_obs_Mb_Ma[observable,i_spring,o_hor,j]), main = pops[j])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, TeX("$Spring\\,Smolt \\rightarrow LGR\\,Survival\\,(HOR)"))
```

@@

```{r eggs-to-parr, fig.width = 6, fig.height = 4}
# extract posterior samples of the BH productivity and capacity parameters
bh_params = post_subset(post, c("alpha", "^beta$"), matrix = T)
### LGR Smolt $\rightarrow O_0$ (NOR)

# extract posterior summaries of total spawners by brood year
Sa_tot = post_summ(post, "^Sa_tot[")
```{r hydro-nor-surv-fit, fig.width = 6, fig.height = 5}
par(oma = c(1.5,1.5,0,0))
plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[.+,origin]$", origin = o_nor)), expit(jags_data$Lphi_obs_Ma_O0[observable,o_nor]), main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,Survival\\,(NOR)"))
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

# extract posterior summaries of total egg production by brood year
f_tot = post_summ(post, "^f_tot[")
### LGR Smolt $\rightarrow O_0$ (HOR)

# extract posterior summaries of total parr recruits by brood year
Pb = post_summ(post, "^Pb[")
```{r hydro-hor-surv-fit, fig.width = 6, fig.height = 5}
par(oma = c(1.5,1.5,0,0))
plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[.+,origin]$", origin = o_hor)), expit(jags_data$Lphi_obs_Ma_O0[observable,o_hor]), main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,Survival\\,(HOR)"))
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

# predict parr recruits along a sequence of spawner abundances
Sa_pred = seq(0, max(Sa_tot[5,]), length = 30)
f_pred = seq(0, max(f_tot[5,]), length = 30)
## Composition Data {.tabset .tabset-pills .tabset-fade}

Pb_pred = t(sapply(1:post_dim(post, "saved"), function(i) BH(f_pred, bh_params[i,1], bh_params[i,2])))
colnames(Pb_pred) = paste0("Pb_pred[", 1:length(Sa_pred), "]")
Pb_pred = post_convert(cbind(postpack:::id_mat(post), Pb_pred))
Pb_pred = post_summ(Pb_pred, "Pb_pred")
Within a single year, the values across all panels sum to one.

# fit ordinary least squares version
ols_fit = fit_fecund_BH(jags_data)$BH_fit
### Weir Sampling {.tabset .tabset-pills}

```{r weir-comp-fit-func}
weir_comp_fit_plot = function(j) {
  # calculate observed q
  q_obs = t(apply(jags_data$weir_x_obs[,,j], 1, function(y) y/sum(y)))

  par(mfcol = c(3,4), oma = c(1.5,1.5,0,0))#, mar = c(1.5,1.5,1.5,0.5))
  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,1,pop]$", pop = j)), q_obs[observable,1], main = TeX("$Female\\,Age\\,3\\,(NOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,2,pop]$", pop = j)), q_obs[observable,2], main = TeX("$Female\\,Age\\,4\\,(NOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,3,pop]$", pop = j)), q_obs[observable,3], main = TeX("$Female\\,Age\\,5\\,(NOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,4,pop]$", pop = j)), q_obs[observable,4], main = TeX("$Male\\,Age\\,3\\,(NOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,5,pop]$", pop = j)), q_obs[observable,5], main = TeX("$Male\\,Age\\,4\\,(NOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,6,pop]$", pop = j)), q_obs[observable,6], main = TeX("$Male\\,Age\\,5\\,(NOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,7,pop]$", pop = j)), q_obs[observable,7], main = TeX("$Female\\,Age\\,3\\,(HOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,8,pop]$", pop = j)), q_obs[observable,8], main = TeX("$Female\\,Age\\,4\\,(HOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,9,pop]$", pop = j)), q_obs[observable,9], main = TeX("$Female\\,Age\\,5\\,(HOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,10,pop]$", pop = j)), q_obs[observable,10], main = TeX("$Male\\,Age\\,3\\,(HOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,11,pop]$", pop = j)), q_obs[observable,11], main = TeX("$Male\\,Age\\,4\\,(HOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,12,pop]$", pop = j)), q_obs[observable,12], main = TeX("$Male\\,Age\\,5\\,(HOR)$"))

  mtext(side = 1, outer = T, line = 0.25, "Brood Year")
  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
}
```

# draw 1000 random parameters
ols_params = exp(rmvnorm(1000, coef(ols_fit), vcov(ols_fit)))
#### CAT

# calculate predicted curve at each pair/summarize
ols_R_pred = t(sapply(1:1000, function(i) BH(f_pred, ols_params[i,1], ols_params[i,2])))
ols_R_pred = apply(ols_R_pred, 2, function(x) quantile(x, c(0.5, 0.025, 0.975)))
```{r cat-weir-comp-fit, fig.width = 8, fig.height = 5}
weir_comp_fit_plot(1)
```

# graphical parameters
par(mar = c(3,3,1,1), mgp = c(2,0.3,0), tcl = -0.2)
#### LOS

# empty plot
plot(1, 1, type = "n", xlim = range(0, f_tot[5,]), ylim = range(0, Pb[5,], Pb_pred[5,]),
     xlab = "Total Egg Production (millions)", ylab = "Parr Recruits", xaxt = "n")
```{r lost-weir-comp-fit, fig.width = 8, fig.height = 5}
weir_comp_fit_plot(2)
```

x_ticks = axisTicks(par("usr")[1:2], log = F)
axis(side = 1, at = x_ticks, labels = x_ticks/1e6)
#### MIN

# draw fitted relationship: Bayesian
polygon(c(f_pred, rev(f_pred)), c(Pb_pred[4,], rev(Pb_pred[5,])), col = alpha("salmon", 0.5), border = NA)
lines(Pb_pred[4,] ~ f_pred, col = "red", lty = 2)
lines(Pb_pred[5,] ~ f_pred, col = "red", lty = 2)
```{r min-weir-comp-fit, fig.width = 8, fig.height = 5}
weir_comp_fit_plot(3)
```

# draw fitted relationship: OLS
polygon(c(f_pred, rev(f_pred)), c(ols_R_pred[2,], rev(ols_R_pred[3,])), col = alpha("grey", 0.5), border = NA)
lines(ols_R_pred[1,] ~ f_pred, lwd = 2)
lines(ols_R_pred[2,] ~ f_pred, lty = 2)
lines(ols_R_pred[3,] ~ f_pred, lty = 2)
lines(Pb_pred[3,] ~ f_pred, col = "red", lwd = 2)
#### UGR

# draw state pairs + uncertainty
segments(f_tot[4,], Pb[3,], f_tot[5,], Pb[3,], col = "red")
segments(f_tot[3,], Pb[4,], f_tot[3,], Pb[5,], col = "red")
points(Pb[3,] ~ f_tot[3,], pch = 21, col = "red", bg = alpha("salmon", 0.5))
```{r ugr-weir-comp-fit, fig.width = 8, fig.height = 5}
weir_comp_fit_plot(4)
```

## Total Eggs vs. Total Spawners
### Carcass Sampling {.tabset .tabset-pills}

This figure illustrates that total spawners is a reasonable index of total egg production. The three lines illustrate the relationship if each spawner (regardless of age/sex) had a fixed number of eggs.
```{r carc-comp-fit-func}
carc_comp_fit_plot = function(j) {

  # calculate observed q
  q_obs = t(apply(jags_data$carc_x_obs[,,j], 1, function(y) y/sum(y)))

  par(mfcol = c(3,4), oma = c(1.5,1.5,0,0))#, mar = c(1.5,1.5,1.5,0.5))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,1,pop]$", pop = j)), q_obs[observable,1], main = TeX("$Female\\,Age\\,3\\,(NOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,2,pop]$", pop = j)), q_obs[observable,2], main = TeX("$Female\\,Age\\,4\\,(NOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,3,pop]$", pop = j)), q_obs[observable,3], main = TeX("$Female\\,Age\\,5\\,(NOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,4,pop]$", pop = j)), q_obs[observable,4], main = TeX("$Male\\,Age\\,3\\,(NOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,5,pop]$", pop = j)), q_obs[observable,5], main = TeX("$Male\\,Age\\,4\\,(NOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,6,pop]$", pop = j)), q_obs[observable,6], main = TeX("$Male\\,Age\\,5\\,(NOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,7,pop]$", pop = j)), q_obs[observable,7], main = TeX("$Female\\,Age\\,3\\,(HOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,8,pop]$", pop = j)), q_obs[observable,8], main = TeX("$Female\\,Age\\,4\\,(HOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,9,pop]$", pop = j)), q_obs[observable,9], main = TeX("$Female\\,Age\\,5\\,(HOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,10,pop]$",pop = j)), q_obs[observable,10], main = TeX("$Male\\,Age\\,3\\,(HOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,11,pop]$",pop = j)), q_obs[observable,11], main = TeX("$Male\\,Age\\,4\\,(HOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,12,pop]$",pop = j)), q_obs[observable,12], main = TeX("$Male\\,Age\\,5\\,(HOR)$"))
  mtext(side = 1, outer = T, line = 0.25, "Brood Year")
  mtext(side = 2, outer = T, line = 0.25, "Proportion of Carcasses")
}
```

```{r, fig.width = 6, fig.height = 4}
# extract posterior summaries of total egg production by brood year
f_tot = post_summ(post, "^f_tot[")
#### CAT

# extract posterior summaries of total spawners by brood year
Sa_tot = post_summ(post, "^Sa_tot[")
```{r cat-carc-comp-fit, fig.width = 8, fig.height = 5}
carc_comp_fit_plot(1)
```

par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(3,3,1,1))
plot(f_tot["mean",] ~ Sa_tot["mean",],
     ylim = c(0, max(f_tot["97.5%",])),
     xlim = c(0, max(Sa_tot["97.5%",])), type = "n",
     ylab = "Total Egg Production (Millions)", xlab = "Total Spawners", las = 1, yaxt = "n")
y_ticks = axisTicks(par("usr")[3:4], log = F)
axis(side = 2, at = y_ticks, labels = y_ticks/1e6, las = 2)
#### LOS

segments(Sa_tot["2.5%",], f_tot["mean",], Sa_tot["97.5%",], f_tot["mean",], col = alpha("red", 0.5))
segments(Sa_tot["mean",], f_tot["2.5%",], Sa_tot["mean",], f_tot["97.5%",], col = alpha("red", 0.5))
points(f_tot["mean",] ~ Sa_tot["mean",], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
abline(c(0, 1000), lty = 1)
abline(c(0, 1800), lty = 2)
abline(c(0, 3600), lty = 3)
legend("bottomright", title = "If Each Spawner Had:",
       legend = c("1000 Eggs", "1800 Eggs", "3600 Eggs"),
       lty = c(1,2,3), bty = "n")
```{r lost-carc-comp-fit, fig.width = 8, fig.height = 5}
carc_comp_fit_plot(2)
```

@@

This figure shows the inherent density dependence built in to the Beverton-Holt recruitment function: with increasing egg density, survival per egg decreases. The horizontal line/region shows the theoretical maximum ($\alpha$) in the absence of density dependence.
#### MIN

```{r, fig.width = 6, fig.height = 4}
# extract posterior summaries of total egg production by brood year
f_tot = post_summ(post, "^f_tot[")
```{r min-carc-comp-fit, fig.width = 8, fig.height = 5}
carc_comp_fit_plot(3)
```

# extract posterior summaries of total parr recruits by brood year
Pb = post_summ(post, "^Pb[")
#### UGR

# conversion rates
Pb_per_f_tot = post_summ(post, "^Pb_per_f_tot[")
```{r ugr-carc-comp-fit, fig.width = 8, fig.height = 5}
carc_comp_fit_plot(4)
```

# max survival
alpha = post_summ(post, "^alpha")
## Spawn Status Data

par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(3,3,1,1))
plot(Pb_per_f_tot["mean",] ~ f_tot["mean",],
     ylim = c(0, max(Pb_per_f_tot["97.5%",], alpha["97.5%",])),
     xlim = c(0, max(f_tot["97.5%",])), type = "n",
     ylab = "Parr per Egg", xlab = "Total Egg Production (Millions)", las = 1, xaxt = "n")
x_ticks = axisTicks(par("usr")[1:2], log = F)
axis(side = 1, at = x_ticks, labels = x_ticks/1e6)
```{r spawn-status-fits, fig.width = 8, fig.height = 5}
par(oma = c(2,2,0,0))
layout(matrix(1:(jags_data$nj * 2), 2, jags_data$nj), heights = c(1, 0.65))
